Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-20 manuscripts/paper-1/main.tex
Achknowledgement + Email remaning

    \author{Georg Hackenberg\inst{1}
    \and
    Alican Tüzün\inst{1}
    }
    \institute{School of Engineering\\
    University of Applied Sciences Upper Austria\\
    4600 Wels, Upper Austria, Austria\\
    \email{lncs@springer.com}}

@@

    The notion of the digital twin, which has gained popularity in 
    recent years, is often subject to vague and ambiguous envisions\cite{Review1}.
    The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't\cite{GrievesApollo13}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during the operation, and can be argued to be similar. 
    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronization was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state\cite{AMRC}.
    In contrast, a digital twin is a virtual counterpart of a real system, which should 
    be synchronized with a selected frequency and fidelity\cite{Review1,Review2,digitaltwinconsortium2022}.

    The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
    and later referenced in a 2005 journal article~\cite{2005JournayArticle}. 
    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
    The goal was to gather enhanced information about the real system to minimize the waste of the system's sources such as energy, 
    time and material. Initially, this model had four main parts. The real system, 
    virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
    Later, Grieves removed the latter, to simplify the model\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
    Grieves decided to use the NASA-invented "Digital Twin" word, instead of the information mirroring model\cite{Originsofdigitaltwinconcept}.

    In recent years, there is evidence that digital twins play a crucial role in the manufacturing industries, 
    life sciences, healthcare, infrastructure and smart cities\cite{Review2}.
    For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
    which was used to collect and analyze the data from the real system for making the process of the real system more efficient~\cite{GeneralElectricWindTurbine}. 
    Another fascinating example of the use of digital twins is Philips' virtual heart model. The twin of the heart evolves with the data generated by ultrasonic sensors to calculate 
    how well the real heart is pumping the blood. This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment~\cite{PhilipsHearth}. 
    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments~\cite{FELICE}.

    The previous studies predominantly focused on the design and implementation of digital twins\cite{Review1, Review2}. 
    However, a crucial aspect that remains unclear is how to achieve quality in these highly intricate and evolvable systems. 
    Therefore, ascertaining the requisite level of quality of a digital twin is an arduous undertaking that requires further research.

    This paper aims not only to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with them~\cite{FELICE}. 
    also, targets to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
    a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module. 
    To evaluate these artifacts, we considered five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.

    \section{State of the art on quality}
    The Oxford English Dictionary defines the word "quality" as a noun or an adjective form. The adjective form indicates, 
    a high standard of excellence as in  "quality products" \cite{OxfordDictionary}. Even though the noun form is defined in multiple ways, the most impactful 
    definition refers to a  standard of an entity that is measured relative to other entities, whether different or similar \cite{OxfordDictionary}.  
    Additionally, quality is the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.
    Both of these definitions clearly show the relative aspect of quality, and the following subcategories are the specialization of these definitions.
    \subsection{Product quality}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. 
    A product can be a physical system like a car, or an abstract system, like a digital twin. Furthermore, product quality is comprised of two aspects~\cite{GrievesPLMBook}.  
    Firstly, quality is an attribute of a product, which refers to the degree to which a product meets its specifications. These product specifications are mostly defined by the supra-systems' subsystems, such as the stakeholders.
    For this aspect, if the stakeholders' expectations or needs are met,  high quality is considered. The second aspect of product quality is the ability to execute to a specific usage standard.
    Unlike the first aspect, standardization is not controllable. Therefore, the product's quality is determined by how well the implied or obligatory standards are met~\cite{GrievesPLMBook}.

    \subsection{Software quality}
    Software is a combination of programs and data that can be utilized by both virtual and physical systems, 
    such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set~\cite{IEE730-2014}. 
    As an example, ISO/IEC:25010 has standardized eight attributes, 
    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality.

    \subsection{Simulation Quality}
    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system 
    \cite{MobusSystemTheory}. However, these days, many simulation processes are done by virtual systems. For example,  software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users 
    to build a simulation model to make predictions and get information about the past- as well as the current state of the system.

    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications. 
    On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation,VerificationValidationSergent}. 
    These techniques are broadly categorized into six areas: informal, static, dynamic, 
    symbolic, constraint, and formal techniques \cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used \cite{balcicategories}.

@@

    He Zhang et al. introduced the updating method for digital twin models in yet another insightful article.
    Once more, the accuracy and coherence of the model concepts were addressed~\cite{ZHANGUPDATEMETHOD}.

    Selch et al. presented a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
    The unique aspect of this study is that the authors determined the contributions of subsystems to forecast the overall quality of the digital twin, 
    rather than just analyzing it as a single system. The digital couplings, which are linkages between the subsystems, are also identified as a source of extra uncertainty. 
    However, since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.

@@

    %%TODO
    \textbf{Discrete Event Simulation Model} consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section. 
    The animation sections provided a two-dimensional and a three-dimensional representation of the system, 
    which aided in understanding the simulation and debugging purposes. The input sections allowed for the management of inputs to the simulation model, and the output section displayed summary performance indicators about the simulation run. 
    The process logic section contained the process building blocks, such as queues and assembly operations. Lastly, the database section provided an interface to data sources and sinks.

@@

    %%TODO
    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
    (Figure~\ref{fig:CorrectnessAndCompleteness}). Additionally, subaspects of completeness, which are \textit{incompleteness} and \textit{overcompleteness} 
    were inspected but identified as a completeness issue.

@@

    \begin{figure}[htbp]
        \includegraphics[width = 1\textwidth]{Evolvability.png}
        \caption{Evolvability has been demonstrated with simplified finite state machines. 
        Evolving the machines on the left side, needed effort 
        and the evolved finite state machines on the right side can be observed.}~\label{fig:Evolvability}
    \end{figure}

    \subsection{Mapping Digital Twin Attributes to Manual Review Results}
    To evaluate the quality of the artifact, the issues were mapped to digital twin attributes. 
    To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:RequirementSpecifications}).

    \subsection{Artifact Quality Evaluation}
    To evaluate the quality of the digital twin artifacts, the mapped findings were scrutinized and evaluated. 
    The process started by identifying which quality attribute(s) were mapped. 
    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:RequirementSpecifications}).

    \begin{figure}[htbp]
        \includegraphics[scale = 0.30]{RequirementSpecifications.png}
        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}
        \label{fig:Method}
    \end{figure}

    \subsection{Digital Twin Quality Evaluation}
    To determine the quality of the digital twin, 
    the values obtained from evaluating each artifact's quality were collected and summed. 
    Furthermore, the value of the sum was assigned to the related digital twin quality attribute. 
    As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:DigitalTwinQuality}).

    \begin{figure}[htbp]
        \includegraphics[scale = 0.25]{DigitalTwinQuality.png}
            \caption{Method for the evaluation of the digital twin quality}
        \label{fig:MethodforDigitalTwinQuality}
    \end{figure}

@@

    \begin{figure}[htbp]
            \centering
            \includegraphics[scale = 0.35]{quality_inspection_results_with_artifacts.png}
            \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in section~\ref{section:Artifacts}, 
            Y-Axis represents the number of missing quality attributes found for each artifact, 
            and lastly, each digital twin quality attribute is shown by the colors.}
            \label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}

@@

    \section*{Acknowledgements}
    TODO

>>>>

    \author{Georg Hackenberg\inst{1}
    \and
    Alican Tüzün\inst{1}
    }
    \institute{School of Engineering\\
    University of Applied Sciences Upper Austria\\
    4600 Wels, Upper Austria, Austria\\
    %%TODO EMAIL
    \email{lncs@springer.com}}

@@

    The notion of the digital twin, which has gained popularity in 
    recent years, is often subject to vague and ambiguous envisions~\cite{Review1}.
    The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesApollo13}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during the operation, and can be argued to be similar. 
    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronization was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state~\cite{AMRC}.
    In contrast, a digital twin is a virtual counterpart of a real system, which should 
    be synchronized with a selected frequency and fidelity~\cite{Review1,Review2,digitaltwinconsortium2022}.

    The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
    and later referenced in a 2005 journal article~\cite{2005JournayArticle}. 
    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
    The goal was to gather enhanced information about the real system to minimize the waste of the system's sources such as energy, 
    time and material. Initially, this model had four main parts. The real system, 
    virtual system, connection between the real and virtual system and virtual simulations~\cite{GrievesPLMBook}. 
    Later, Grieves removed the latter, to simplify the model~\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
    Grieves decided to use the NASA-invented `Digital Twin' word, instead of the information mirroring model~\cite{Originsofdigitaltwinconcept}.

    In recent years, there is evidence that digital twins play a crucial role in the manufacturing industries, 
    life sciences, healthcare, infrastructure and smart cities~\cite{Review2}.
    For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
    which was used to collect and analyze the data from the real system for making the process of the real system more efficient~\cite{GeneralElectricWindTurbine}. 
    Another fascinating example of the use of digital twins is Philips' virtual heart model. The twin of the heart evolves with the data generated by ultrasonic sensors to calculate 
    how well the real heart is pumping the blood. This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment~\cite{PhilipsHearth}. 
    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments~\cite{FELICE}.

    The previous studies predominantly focused on the design and implementation of digital twins~\cite{Review1, Review2}. 
    However, a crucial aspect that remains unclear is how to achieve quality in these highly intricate and evolvable systems. 
    Therefore, ascertaining the requisite level of quality of a digital twin is an arduous undertaking that requires further research.

    This paper aims not only to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with them~\cite{FELICE},  
    but also, targets to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
    a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module. 
    To evaluate these artifacts, we considered five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.

    \section{State of the art on quality}
    The Oxford English Dictionary defines the word `quality' as a noun or an adjective form. The adjective form indicates, 
    a high standard of excellence as in  `quality products`~\cite{OxfordDictionary}. Even though the noun form is defined in multiple ways, the most impactful 
    definition refers to a  standard of an entity that is measured relative to other entities, whether different or similar~\cite{OxfordDictionary}.  
    Additionally, quality is the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.
    Both of these definitions clearly show the relative aspect of quality, and the following subcategories are the specialization of these definitions.
    \subsection{Product quality}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. A product can be a physical system like a car, or an abstract system, like a digital twin. Furthermore, 
    product quality is comprised of two aspects~\cite{GrievesPLMBook}.  
    Firstly, quality is an attribute of a product, which refers to the degree to which a product meets its specifications. These product specifications are mostly defined by the supra-systems' subsystems, such as the stakeholders.
    For this aspect, if the stakeholders' expectations or needs are met,  high quality is considered. The second aspect of product quality is the ability to execute to a specific usage standard.
    Unlike the first aspect, standardization is not controllable. Therefore, the product's quality is determined by how well the implied or obligatory standards are met~\cite{GrievesPLMBook}.

    \subsection{Software quality}
    Software is a combination of programs and data that can be utilized by both virtual and physical systems, 
    such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set~\cite{IEE730-2014}. 
    As an example, ISO/IEC:25010 has standardized eight attributes, 
    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality~\cite{ISO/IEC:25010}.

    \subsection{Simulation Quality}
    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system~\cite{MobusSystemTheory}.
    However, these days, many simulation processes are done by virtual systems. For example, software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users 
    to build a simulation model to make predictions and get information about the past- as well as the current state of the system.

    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
    Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications.
     On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation,VerificationValidationSergent}. 
    These techniques are broadly categorized into six areas: informal, static, dynamic, 
    symbolic, constraint, and formal techniques~\cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used~\cite{balcicategories}.

@@

    In yet another insightful article, He Zhang et al. introduced the updating method for digital twin models.
    Once more, the accuracy and coherence of the model concepts were addressed~\cite{ZHANGUPDATEMETHOD}.

    Furthermore, Selch et al. presented a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
    The unique aspect of this study is that the authors determined the contributions of subsystems to forecast the overall quality of the digital twin, 
    rather than just analyzing it as a single system. The digital couplings, which are linkages between the subsystems, are also identified as a source of extra uncertainty. 
    However, since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.

@@

    \textbf{Discrete Event Simulation Model} consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section. 
    The animation sections provided a two-dimensional and a three-dimensional representation of the system, 
    which aided in understanding the simulation and debugging purposes. The input sections allowed for the management of inputs to the simulation model, and the output section displayed summary performance indicators about the simulation run. 
    The process logic section contained the process building blocks, such as queues and assembly operations. Lastly, the database section provided an interface to data sources and sinks.

@@

    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
    (Figure~\ref{fig:CorrectnessAndCompleteness}). Additionally, subaspects of completeness, which are \textit{incompleteness} and \textit{overcompleteness} 
    were inspected but identified as a completeness issue.

@@

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Evolvability.png}
        \caption{Evolvability has been demonstrated with simplified finite state machines. 
        Evolving the machines on the left side, needed effort 
        and the evolved finite state machines on the right side can be observed.}~\label{fig:Evolvability}
    \end{figure}

    \subsection{Mapping Digital Twin Attributes to Manual Review Results}
    To evaluate the quality of the artifact, the issues were mapped to digital twin attributes. 
    To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:Method}).

    \subsection{Artifact Quality Evaluation}
    To evaluate the quality of the digital twin artifacts, the mapped findings were scrutinized and evaluated. 
    The process started by identifying which quality attribute(s) were mapped. 
    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:Method}).

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8\textwidth]{RequirementSpecifications.png}
        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}\label{fig:Method}
    \end{figure}

    \subsection{Digital Twin Quality Evaluation}
    To determine the quality of the digital twin, 
    the values obtained from evaluating each artifact's quality were collected and summed. 
    Furthermore, the value of the sum was assigned to the related digital twin quality attribute. 
    As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:MethodforDigitalTwinQuality}).

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8\textwidth]{DigitalTwinQuality.png}
            \caption{Method for the evaluation of the digital twin quality}\label{fig:MethodforDigitalTwinQuality}
    \end{figure}

@@

    \begin{figure}[htbp]
            \centering
            \includegraphics[scale = 0.35]{quality_inspection_results_with_artifacts.png}
            \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in section~\ref{section:Artifacts}, 
            Y-Axis represents the number of missing quality attributes found for each artifact, 
            and lastly, each digital twin quality attribute is shown by the colors.}\label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}

@@

    \section*{Acknowledgements}
    %TODO
